The Astropy Project

### 2017-11-14 main.tex
Finish affiliated package section

\subsection{Coordination of Astropy}
% draft by ?? (BMS thinks Erik)
% edited by Adrian PW

From its inception, \astropy has required coordination to ensure the project
as a whole and its coding efforts are consistent and reasonably efficient.
While many \python projects adopt a ``Benevolent Dictator For Life'' (BDFL)
model, \astropy has instead opted for a \emph{coordination committee}.  This
is in part due to the nature of the project as a large-scale collaboration
between many contributors with many interests, and in part due to simply the
amount of work that needs to get done.  For the latter reason, the
project has expanded the committee from three to four members starting in
2016.

@@

Central to the success of \astropy is an open environment where anybody can
contribute to the project.
However, this model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces.
Thus, \astropy has a mechanism to more formally propose significant changes to
the core package (e.g., the release cycle; \citealt{ape2}), to plan out major
new features, or institute new organization-wide policies (e.g.,
code of conduct; \citealt{ape8}).
This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
modeled after the ``Python Enhancement Proposals'' (PEP) and guide the
development of the \python programming language.
In an APE one or more authors describe in detail the proposed changes or
additions, including a rationale for the changes, how these changes will be
implemented, and, in the case of code, what the interface will be \citep{ape1}.
The APEs are discussed and refined by the community before much work is invested
into a detailed implementation; anyone is welcome to contribute to these
discussions during the open consideration period by leaving comments on the
respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}}
In previous APEs a community consensus emerged and APEs are accepted and become
the basis for future work at this point.
In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in question.

@@

A major part of the \astropy project is the concept of
``Affiliated Packages''. An affiliated package is an astronomy-related
\python package that is not part of the \astropypkg core package, but
has requested to be included as part of the \astropy project's
community. These packages support the goals and vision of \astropy of
improving code reuse, interoperability, and embracing good coding
practices such as testing and thorough documentation.
Affiliated packages contain functionality that is more specialized,
have license incompatibilities, or have external dependencies (e.g., GUI
libraries) that make these packages more suitable to be separate from the
\astropypkg core package.
Affiliated packages may also be used to develop substantial, new functionality
that will eventually be incorporated into the \astropypkg core package: as
initially separate packages, the typically rapid development or new,
experimental features may benefit from having a release cycle that is not tied
to the \astropypkg core.

\inlinecomment{APW}{This needs to be finished:}
In general we hope that becoming an affiliated package is seen as
a good way for new and existing packages to gain exposure.
%
\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages into the future section below}

>>>>

\subsection{Coordination of Astropy}
% draft by ?? (BMS thinks Erik)
% edited by Adrian PW
\label{sect:coordcom}
From its inception, \astropy has required coordination to ensure the project
as a whole and its coding efforts are consistent and reasonably efficient.
While many \python projects adopt a ``Benevolent Dictator For Life'' (BDFL)
model, \astropy has instead opted for a \emph{coordination committee}.  This
is in part due to the nature of the project as a large-scale collaboration
between many contributors with many interests, and in part due to simply the
amount of work that needs to get done.  For the latter reason, the
project has expanded the committee from three to four members starting in
2016.

@@

Central to the success of \astropy is an open environment where anybody can
contribute to the project.
However, this model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces.
Thus, \astropy has a mechanism to more formally propose significant changes to
the core package (e.g., the release cycle; \citealt{ape2}), to plan out major
new features, or institute new organization-wide policies (e.g.,
code of conduct; \citealt{ape8}).
This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
modeled after the ``Python Enhancement Proposals'' (PEP) that guide the
development of the \python programming language.
In an APE one or more authors describe in detail the proposed changes or
additions, including a rationale for the changes, how these changes will be
implemented, and, in the case of code, what the interface will be \citep{ape1}.
The APEs are discussed and refined by the community before much work is invested
into a detailed implementation; anyone is welcome to contribute to these
discussions during the open consideration period by leaving comments on the
respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}}
In previous APEs a community consensus emerged and APEs are accepted and become
the basis for future work at this point.
In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in question.

@@

A major part of the \astropy project is the concept of
``Affiliated Packages''. An affiliated package is an astronomy-related
\python package that is not part of the \astropypkg core package, but
has requested to be included as part of the \astropy project's
community. These packages support the goals and vision of \astropy of
improving code reuse, interoperability, and embracing good coding
practices such as testing and thorough documentation.
Affiliated packages contain functionality that is more specialized,
have license incompatibilities, or have external dependencies (e.g., GUI
libraries) that make these packages more suitable to be separate from the
\astropypkg core package.
Affiliated packages may also be used to develop substantial, new functionality
that will eventually be incorporated into the \astropypkg core package. 
Initially separate packages with typically rapid initial development and new experimental features benefit from having a release cycle that is not tied
to the \astropypkg core.
Affiliated pacakges are listed on the main astropy website and advertized to the community through astropy mailing lists, so becoming an affiliated package is sa good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality. This process of listing and promoting affiliated packages is one way in which the \astropy project tries to help with code reuse in the astronomical community. Packages can become affilited to \astropy by applying for this status on a public mailing list. The coordination comittee (sect.~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package where possible.
